---
title: 'LAEEG: Connectivity analysis: across time'
author: "Marc Colomer"
date: "8/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries, include= FALSE}
#library(lme4)
library(ez)
library(ggplot2)
library(tidyverse)
library(lmerTest)
path_mac_new <- '/Users/marccolomer/Documents/LAEEG'

```

```{r readdata, include= FALSE}

# Cluster pairs
df_wide_phl_FC <- read.csv("input_analysis_R/T_FC_ispc_time_9m.csv", sep=",")
df_phl_FC_9m <- gather(df_wide_phl_FC, Participant, Connectivity, -Time, - Condition, -Age, -ChannelPair)
df_wide_phl_PC <- read.csv("input_analysis_R/T_PC_ispc_time_9m.csv", sep=",")
df_phl_PC_9m <- gather(df_wide_phl_PC, Participant, Connectivity, -Time, - Condition, -Age, -ChannelPair)
df_wide_phl_OC <- read.csv("input_analysis_R/T_OC_ispc_time_9m.csv", sep=",")
df_phl_OC_9m <- gather(df_wide_phl_OC, Participant, Connectivity, -Time, - Condition, -Age, -ChannelPair)

df_wide_phl_FC <- read.csv("input_analysis_R/T_FC_ispc_time_12m.csv", sep=",")
df_phl_FC_12m <- gather(df_wide_phl_FC, Participant, Connectivity, -Time, - Condition, -Age, -ChannelPair)
df_wide_phl_PC <- read.csv("input_analysis_R/T_PC_ispc_time_12m.csv", sep=",")
df_phl_PC_12m <- gather(df_wide_phl_PC, Participant, Connectivity, -Time, - Condition, -Age, -ChannelPair)
df_wide_phl_OC <- read.csv("input_analysis_R/T_OC_ispc_time_12m.csv", sep=",")
df_phl_OC_12m <- gather(df_wide_phl_OC, Participant, Connectivity, -Time, - Condition, -Age, -ChannelPair)

data_all <- rbind(df_phl_FC_9m, df_phl_PC_9m, df_phl_OC_9m, df_phl_FC_12m, df_phl_PC_12m, df_phl_OC_12m)

# Whole Brain
df_wide_phl_9m <- read.csv("input_analysis_R/T_thres_acrosstime_cl_9m_ispc.csv", sep=",")
df_phl_9m <- gather(df_wide_phl_9m, Participant, Threshold, -Time, - Condition, -Age)
df_wide_phl_12m <- read.csv("input_analysis_R/T_thres_acrosstime_cl_12m_ispc.csv", sep=",")
df_phl_12m <- gather(df_wide_phl_12m, Participant, Threshold, -Time, - Condition, -Age)

data_wb_all <- rbind(df_phl_9m, df_phl_12m)

data_all_OC <- data_all%>%
  filter(ChannelPair == "OC" & Time>-1000 & Time<1000)
data_all_PC <- data_all%>%
  filter(ChannelPair == "PC" & Time>-1000 & Time<1000)
data_all_FC <- data_all%>%
  filter(ChannelPair == "FC" & Time>-1000 & Time<1000)

subj_before_merging <- filter(data_all_OC, Time == -990, Condition == "cane")

# I need to do this because the names are different, and I want them to be exactly the same
thres_wb <- select(data_wb_all,c(Threshold,Participant, Time, Condition))%>%
  mutate(Condition_2 = ifelse(Condition == "Cane", "cane", "grasp"))
thres_wb$Condition <- thres_wb$Condition_2
thres_wb <- select(thres_wb, Participant, Threshold, Time, Condition)

data_all_OC <- merge(data_all_OC, thres_wb, by = c("Participant", "Time", "Condition"))
data_all_PC <- merge(data_all_PC, thres_wb, by = c("Participant", "Time", "Condition"))
data_all_FC <- merge(data_all_FC, thres_wb, by = c("Participant", "Time", "Condition"))

subj_after_merging <- filter(data_all_OC, Time == -990, Condition == "cane")

data_all_with_wb <- rbind(data_all_OC, data_all_PC, data_all_FC)

data_all_with_wb <- data_all_with_wb%>%
  mutate(connectivity_norm = 10*log10(Connectivity/Threshold))

data_all <- data_all_with_wb

## SUMMARY PARTICIPANTS
data_sum_subj <- filter(data_all, Time == 0, ChannelPair == "OC", Condition == "grasp")

## NEW BEHAVIOR CODING FILE:
d_behavior <- read.csv("input_analysis_R/912m_Beh_Marc_121820_HCedit.csv", sep=",")%>%
  pivot_wider(names_from = Condition, values_from = c(Competence_NEW,Competence_include_OneTrial))
d_behavior<- rowid_to_column(d_behavior)

```

### PLOT CONNECTIVITY

## 1. Cane vs Grasp (normalized by mean((connectivity cane + connectivity grasp)./2))

We calculate ISPC across time between chanpairs.
Connectivity values are normalized (subtraction) by the mean connectivity of cane and grasp
Plot connectivity for the following frequency:

- Alpha (6-9Hz)


## 1. CONNECTIVITY ACROSS WINDOWS TIME (average) COMPARING CONDITIONS (SEPARATED BY CHANNEL PAIR): ISPC
```{r alphanorm, echo=FALSE}

lbls <- c('-1000:-500', '-500:0', '0:500', '500:1000')
min_time <- -1000
max_time <- 1000

sum_all_group <- data_all%>%
  filter(Time>min_time & Time <=max_time)%>%
  group_by(Condition, Age, ChannelPair, Time) %>%
  summarise(mean_con = mean(connectivity_norm, na.rm=TRUE), sderr = sd(connectivity_norm, na.rm=TRUE)/sqrt(length(Participant)),
          n_subj = length(Participant))%>%
  group_by(Condition, Age, ChannelPair, TimeGroup = cut(Time, 
               breaks = seq(min_time, max_time, by = 500), labels = lbls))%>%
  summarise(mean_group = mean(mean_con, na.rm=TRUE), sderr_group = mean(sderr))%>%
    mutate(Age_Condition =  paste(Age, "_", Condition))

# LINE PLOTS
sum_all_group$ChannelPair = factor(sum_all_group$ChannelPair, levels=c('FC','PC','OC'))
sum_all_group$Age = factor(sum_all_group$Age, levels=c('9m','12m'))

p1<- ggplot(sum_all_group, aes(x=TimeGroup, y=mean_group, group = Condition, color=Condition)) +
  geom_line()+geom_point()+geom_errorbar(aes(ymin = mean_group-sderr_group, ymax = mean_group+sderr_group), width = .2, position = position_dodge(0.05)) + facet_grid(Age ~ ChannelPair) + ylab("ISPC (relative to WB)") + xlab("Time Window (ms)") + ggtitle("Intra-channel connectivity across time")
p1
ggsave('ispc_acrosstime_condition_chanP&timewin_cl15.png', plot = last_plot(), device = 'png', scale = 0.6, width = 15, height = 7, path = path_mac_new) 

## STATISTICS
sum_all_stats <- data_all%>%
  filter(Time>min_time & Time<=max_time)%>%
  group_by(TimeGroup = cut(Time, 
               breaks = seq(min_time, max_time, by = 500), labels = lbls), Condition, Age, Participant, ChannelPair)%>%
  summarise(mean_stats = mean(connectivity_norm))


# MODEL INCLUDING EVERYTHING
sum_all_stats_fil <- filter(sum_all_stats, TimeGroup == lbls[1] | TimeGroup == lbls[2] | TimeGroup == lbls[3] | TimeGroup == lbls[4])

## POST-HOC CONDITION * CHANNELPAIR
sum_all_stats_oc <- sum_all_stats_fil %>%
  filter(ChannelPair == "OC")

sum_all_stats_fc <- sum_all_stats_fil %>%
  filter(ChannelPair == "FC")

sum_all_stats_pc <- sum_all_stats_fil %>%
  filter(ChannelPair == "PC")

Anova_oc<- ezANOVA(data=sum_all_stats_oc, dv = mean_stats, wid = Participant, within = .(TimeGroup, Condition), between = .(Age), type = 3)
show(Anova_oc)

Anova_fc<- ezANOVA(data=sum_all_stats_fc, dv = mean_stats, wid = Participant, within = .(TimeGroup, Condition), between = .(Age), type = 3)
show(Anova_fc)

Anova_pc<- ezANOVA(data=sum_all_stats_pc, dv = mean_stats, wid = Participant, within = .(TimeGroup, Condition), between = .(Age), type = 3)
show(Anova_pc)

## POST-HOC INTERACTION AGE * TIMEGROUP AT OC CHANNEL PAIR
sum_all_stats_t1 <- sum_all_stats_oc %>%
  filter(TimeGroup == lbls[1])
sum_all_stats_t2 <- sum_all_stats_oc %>%
  filter(TimeGroup == lbls[2])
sum_all_stats_t3 <- sum_all_stats_oc %>%
  filter(TimeGroup == lbls[3])
sum_all_stats_t4 <- sum_all_stats_oc %>%
  filter(TimeGroup == lbls[4])

Anova_t<- ezANOVA(data=sum_all_stats_t1, dv = mean_stats, wid = Participant, between = .(Age), type = 3)
show(Anova_t)
Anova_t<- ezANOVA(data=sum_all_stats_t2, dv = mean_stats, wid = Participant, between = .(Age), type = 3)
show(Anova_t)
Anova_t<- ezANOVA(data=sum_all_stats_t3, dv = mean_stats, wid = Participant, between = .(Age), type = 3)
show(Anova_t)
Anova_t<- ezANOVA(data=sum_all_stats_t4, dv = mean_stats, wid = Participant, between = .(Age), type = 3)
show(Anova_t)

## POST-HOC TRIPLE INTERACTION. SEPARATING BY AGE AND CONDITION
sum_all_stats_t1 <- sum_all_stats_fc %>%
  filter(TimeGroup == lbls[1])
sum_all_stats_t2 <- sum_all_stats_fc %>%
  filter(TimeGroup == lbls[2])
sum_all_stats_t3 <- sum_all_stats_fc %>%
  filter(TimeGroup == lbls[3])
sum_all_stats_t4 <- sum_all_stats_fc %>%
  filter(TimeGroup == lbls[4])

Anova_t<- ezANOVA(data=sum_all_stats_t1, dv = mean_stats, wid = Participant, within = .(Condition), between = .(Age), type = 3)
show(Anova_t)
Anova_t<- ezANOVA(data=sum_all_stats_t2, dv = mean_stats, wid = Participant, within = .(Condition),between = .(Age), type = 3)
show(Anova_t)
Anova_t<- ezANOVA(data=sum_all_stats_t3, dv = mean_stats, wid = Participant, within = .(Condition),between = .(Age), type = 3)
show(Anova_t)
Anova_t<- ezANOVA(data=sum_all_stats_t4, dv = mean_stats, wid = Participant, within = .(Condition),between = .(Age), type = 3)
show(Anova_t)

## Post-hoc to see what happens in the last window
sum_all_stats_9m_t4 <- sum_all_stats_t4 %>%
  filter(Age == "9m")
sum_all_stats_12m_t4 <- sum_all_stats_t4 %>%
  filter(Age == "12m")

Anova_t<- ezANOVA(data=sum_all_stats_9m_t4, dv = mean_stats, wid = Participant, within = Condition, type = 3)
show(Anova_t)
Anova_t<- ezANOVA(data=sum_all_stats_12m_t4, dv = mean_stats, wid = Participant, within = Condition, type = 3)
show(Anova_t)


```


## WHOLE BRAIN!!!!
### PLOT WHOLE BRAIN CONNECTIVITY (10-10 positions)

## a. Cane vs Grasp in specific Time windows (ISPC)

```{r thresholdTheta, echo=FALSE}

  lbls <- c('-1000:-500', '-500:0', 
            '0:500', '500:1000')
  min_time <- -1000
  max_time <- 1000
  sum_phl <- data_wb_all%>%
    filter(Time > min_time & Time < max_time)%>%
    group_by(Time, Age, Condition)%>%
    summarise(mean_1 = mean(Threshold), sderr = sd(Threshold)/sqrt(length(Participant)),
           n_subj = length(Participant))%>%
    group_by(Condition, Age, TimeGroup = cut(Time,
                 breaks = seq(min_time, max_time, by = 500), labels = lbls))%>%
    summarise(mean_group = mean(mean_1, na.rm=TRUE), sderr_group = mean(sderr))%>%
    mutate(Age_Condition =  paste(Age, "_", Condition))
 
      p1<- ggplot(sum_phl, aes(x=TimeGroup, y=mean_group, group = Condition, color=Condition)) + geom_line()+geom_point()+geom_errorbar(aes(ymin = mean_group-sderr_group, ymax = mean_group+sderr_group), width = .2, position = position_dodge(0.05)) + ylab("Whole Brain Connectivity") + xlab("Time Window (ms)") + ylim(0.53, 0.575) + facet_grid(Age ~ .)
  
  p1 
  ggsave('wb_thres_acrosstime_timewin_ispc_cl15.png', plot = last_plot(), device = 'png', scale = 0.75, width = 6, height = 4, path = path_mac_new)
    
     
  p1<- ggplot(sum_phl, aes(x=TimeGroup, y=mean_group, group = Age_Condition, linetype=Age, color=Condition)) + geom_line()+geom_point()+geom_errorbar(aes(ymin = mean_group-sderr_group, ymax = mean_group+sderr_group), width = .2, position = position_dodge(0.05)) + ylab("ISPC Whole Brain") + xlab("Time Window") + ylim(0.53, 0.575)
  
  p1
  ggsave('wb_thres_acrosstime_timewin_ispc_cl15.png', plot = last_plot(), device = 'png', scale = 0.75, width = 6, height = 4, path = path_mac_new)


## STATISTICS
sum_all_stats <- data_wb_all%>%
  filter(Time>min_time & Time<=max_time)%>%
  group_by(TimeGroup = cut(Time, 
               breaks = seq(min_time, max_time, by = 500), labels = lbls), Condition, Age, Participant)%>%
  summarise(mean_stats = mean(Threshold))

Anova <- ezANOVA(data=sum_all_stats, dv = mean_stats, wid = Participant, within = .(Condition, TimeGroup), between = .(Age), type = 3)
show(Anova)

sum_all_stats_t1 <- sum_all_stats %>%
  filter(TimeGroup == lbls[1])

sum_all_stats_t2 <- sum_all_stats %>%
  filter(TimeGroup == lbls[2])

sum_all_stats_t3 <- sum_all_stats %>%
  filter(TimeGroup == lbls[3])

sum_all_stats_t4 <- sum_all_stats %>%
  filter(TimeGroup == lbls[4])

Anova_t1<- ezANOVA(data=sum_all_stats_t1, dv = mean_stats, wid = Participant, within = .(Condition), between = .(Age), type = 3)
show(Anova_t1)

Anova_t2<- ezANOVA(data=sum_all_stats_t2, dv = mean_stats, wid = Participant, within = .(Condition), between = .(Age), type = 3)
show(Anova_t2)

Anova_t3<- ezANOVA(data=sum_all_stats_t3, dv = mean_stats, wid = Participant, within = .(Condition), between = .(Age), type = 3)
show(Anova_t3)

Anova_t4<- ezANOVA(data=sum_all_stats_t4, dv = mean_stats, wid = Participant, within = .(Condition), between = .(Age), type = 3)
show(Anova_t4)

```


## CORRELATE CONNECTIVITY (ISPC across time normalized by whole brain threshold) AND BEHAVIOR

```{r thetanormWB, echo=FALSE}

## SUMMARIZE DATA
lbls <- c('-1000:-500', '-500:0', 
          '0:500', '500:1000')

min_time <- -1000
max_time <- 1000

sum_all_stats <- data_all_with_wb%>%
  filter(Time>min_time & Time<=max_time)%>%
  group_by(TimeGroup = cut(Time, 
               breaks = seq(min_time, max_time, by = 500), labels = lbls), Condition, Age, Participant, ChannelPair)%>%
  summarise(mean_stats = mean(connectivity_norm))

sum_all_stats_t2 <- sum_all_stats %>%
  filter(TimeGroup == lbls[1])

######################################################################
######################################################################
## LINK TO BEHAVIOR

## FIRST, PREPARE DATA

sum_all_stats_wide<- sum_all_stats_t2 %>%
  pivot_wider(names_from = c(Condition,ChannelPair), values_from = mean_stats)%>%
  arrange(desc(Age)) # BE CAREFUL WITH THIS. MAKE SURE THAT THE ORDER IS THE SAME AS IN d_behavior

sum_all_stats_wide<- rowid_to_column(sum_all_stats_wide)

d_con_beh <- merge(sum_all_stats_wide,d_behavior, by = "rowid")%>%
  select(-c(TimeGroup, rowid, subnum))%>%
  pivot_longer(
  cols = cane_FC:grasp_PC,
  names_to = "Condition.ChanPair",
  values_to = "Connectivity")%>%
  separate(Condition.ChanPair,c("Condition", "ChanPair"))%>%
  mutate(GraspLat = Competence_NEW_Grasp/1000)%>%
  mutate(CaneLat = Competence_NEW_Cane/1000)

## NOW, LINK IT TO BEHAVIOR
## 1. GRASP LATENCY
d_con_beh_noNaN <- d_con_beh[!is.na(d_con_beh$GraspLat),]
  
p_data <- ggplot(d_con_beh_noNaN, aes(x=GraspLat, y=Connectivity, fill = Age, color = Age)) +
  geom_point(shape=1) +     # Use hollow circles
  geom_smooth(method=lm) + facet_grid(. ~ ChanPair) + ylab("ISPC anticipation") + xlab("Grasp Latency (s)")
p_data 
ggsave('GraspLatVSispc_normWB_acrosstime_-1000-500_Age_noCond_cl15.png', plot = last_plot(), device = 'png', scale = 0.6, width = 13, height = 7, path = path_mac_new)

## MIXED-EFFECTS GRASP COMPETENCE AND CONNECTIVITY
d_con_beh_oc <- d_con_beh_noNaN %>%
  filter(ChanPair == "OC")
d_con_beh_fc <- d_con_beh_noNaN %>%
  filter(ChanPair == "FC")
d_con_beh_pc <- d_con_beh_noNaN %>%
  filter(ChanPair == "PC")


## MIXED EFFECT MODELS
# BASIC MODEL = O-C
m.0 <- lmer(Connectivity ~ (1 | Participant) , data=d_con_beh_oc, REML = FALSE)  # build

# ADD THE NEXT MORE "OBVIOUS" VARIABLE
m.0_1 <- update(m.0, .~. + Age) 
m.1_0 <- update(m.0_1, .~. + Condition) 
m.1_1 <- update(m.1_0, .~. + Age:Condition)

m.2_0 <- update(m.1_1, .~. + GraspLat)
m.2_1 <- update(m.2_0, .~. + GraspLat:Condition)
m.2_2 <- update(m.2_0, .~. + GraspLat:Age)
m.2_3 <- update(m.2_0, .~. + GraspLat:Age:Condition)

anova(m.0,m.0_1,m.1_0,m.1_1,m.2_0,m.2_1, m.2_3) 
anova(m.2_0)
summary(m.2_0)

## BASED ON SIGNIFICANT EFFECTS (OR MARGINALLY SIGNIFICANT) BUILD MODELS FOR THE CONTROL NETWORKS
# BASIC MODEL = F-C
m.0 <- lmer(Connectivity ~  (1 | Participant) , data=d_con_beh_fc, REML = FALSE)  # build

# ADD THE NEXT MORE "OBVIOUS" VARIABLE
m.0_1 <- update(m.0, .~. + Condition) 
m.1_0 <- update(m.0_1, .~. + Age) 
m.2_0 <- update(m.1_0, .~. + GraspLat) 
anova(m.0,m.0_1,m.1_0,m.2_0)

# BASIC MODEL = P-C
m.0 <- lmer(Connectivity ~ (1 | Participant), data=d_con_beh_pc, REML = FALSE)  # build

# ADD THE NEXT MORE "OBVIOUS" VARIABLE
m.0_1 <- update(m.0, .~. + Condition) 
m.1_0 <- update(m.0_1, .~. + Age) 
m.2_0 <- update(m.1_0, .~. + GraspLat) 
anova(m.0,m.0_1,m.1_0,m.2_0)


## 3. CANE LATENCY
d_con_beh_noNaN <- d_con_beh[!is.na(d_con_beh$CaneLat),]

p_data <- ggplot(d_con_beh_noNaN, aes(x=CaneLat, y=Connectivity, shape=Age, colour=Age, fill=Age)) +
  geom_point(shape=1) +     # Use hollow circles
  geom_smooth(method=lm) + facet_grid(. ~ ChanPair) + ylab("ISPC anticipation") + xlab("Cane Latency (s)")
p_data 
ggsave('ispcVSCaneLat_normWB_acrosstime_-1000-500_age_noCond_cl15.png', plot = last_plot(), device = 'png', scale = 0.8, width = 11, height = 6, path = path_mac_new)

## LINEAR MODEL GRASP COMPETENCE AND CONNECTIVITY
# LINEAR MODEL
d_con_beh_oc <- d_con_beh_noNaN %>%
  filter(ChanPair == "OC")
d_con_beh_fc <- d_con_beh_noNaN %>%
  filter(ChanPair == "FC")
d_con_beh_pc <- d_con_beh_noNaN %>%
  filter(ChanPair == "PC")

## MIXED EFFECT MODELS
# BASIC MODEL = O-C
m.0 <- lmer(Connectivity ~ (1 | Participant) , data=d_con_beh_pc, REML = FALSE)  # build

# ADD THE NEXT MORE "OBVIOUS" VARIABLE
m.0_1 <- update(m.0, .~. + Condition) 
m.1_0 <- update(m.0_1, .~. + Age) 
m.1_1 <- update(m.1_0, .~. + Age:Condition)

m.2_0 <- update(m.1_1, .~. + CaneLat) 
m.2_1 <- update(m.2_0, .~. + CaneLat:Age)
m.2_2 <- update(m.2_0, .~. + CaneLat:Condition)
m.2_3 <- update(m.2_0, .~. + CaneLat:Age:Condition)

anova(m.0,m.0_1,m.1_0,m.1_1,m.2_0,m.2_1, m.2_3)

# Check if grasp competence and cane competence are correlated
d_behavior_fil <- d_behavior[!is.na(d_behavior$Competence_NEW_Cane),]
lm_out <- lm(Competence_NEW_Cane ~ Competence_NEW_Grasp , data=d_behavior_fil, REML = FALSE)  # build
summary(lm_out)

```

## ADDITIONAL ANALYSIS NOT INCLUDED IN THE MAIN MANUSCRIPT:
# 1. Similar to previous analysis, but looking at the group level (separating infants by their competence using the median)

```{r barplot_median, echo=FALSE}

## SUMMARIZE DATA
lbls <- c('-1000:-500', '-500:0', 
          '0:500', '500:1000')

min_time <- -1000
max_time <- 1000

sum_all_stats <- data_all_with_wb%>%
  filter(Time>min_time & Time<=max_time)%>%
  group_by(TimeGroup = cut(Time, 
               breaks = seq(min_time, max_time, by = 500), labels = lbls), Condition, Age, Participant, ChannelPair)%>%
  summarise(mean_stats = mean(connectivity_norm))

sum_all_stats_t2 <- sum_all_stats %>%
  filter(TimeGroup == lbls[1])

######################################################################
######################################################################
## LINK TO BEHAVIOR

## FIRST, PREPARE DATA

sum_all_stats_wide<- sum_all_stats_t2 %>%
  pivot_wider(names_from = c(Condition,ChannelPair), values_from = mean_stats)%>%
  arrange(desc(Age)) # BE CAREFUL WITH THIS. MAKE SURE THAT THE ORDER IS THE SAME AS IN d_behavior

sum_all_stats_wide<- rowid_to_column(sum_all_stats_wide)

d_con_beh <- merge(sum_all_stats_wide,d_behavior, by = "rowid")%>%
  select(-c(TimeGroup, rowid, subnum))%>%
  pivot_longer(
  cols = cane_FC:grasp_PC,
  names_to = "Condition.ChanPair",
  values_to = "Connectivity")%>%
  separate(Condition.ChanPair,c("Condition", "ChanPair"))%>%
  mutate(GraspLat = Competence_NEW_Grasp/1000)%>%
  mutate(CaneLat = Competence_NEW_Cane/1000)

median_comp <- median(d_con_beh$GraspLat[which(!is.na(d_con_beh$GraspLat))])

## NOW, LINK IT TO BEHAVIOR

## FIRST BAR PLOT only with OC (what will go in the paper)
d_con_beh_noNaN <- d_con_beh[!is.na(d_con_beh$GraspLat),]%>%
  filter(ChanPair == "OC")%>%
  mutate(group_competence = ifelse(GraspLat > median_comp, "Slow", "Fast"))%>%
  group_by(Condition, group_competence)%>%
  summarise(Connectivity_mean = mean(Connectivity), sd_c = sd(Connectivity)/sqrt(length(Participant)), sd = sd(Connectivity))

d_con_beh_noNaN2 <- d_con_beh_noNaN%>%
  mutate(Condition2 = ifelse(Condition == "cane", "Novel", "Familiar"))%>%
  within(Condition2 <- factor(Condition2, levels=names(sort(table(Condition2), decreasing=FALSE))))

d_con_beh_noNaN2$Condition2 <- factor(d_con_beh_noNaN2$Condition2, levels=c('Novel','Familiar'))

p_bar <- ggplot(d_con_beh_noNaN2, aes(x=group_competence, y=Connectivity_mean, fill=Condition2)) + geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Connectivity_mean-sd_c, ymax=Connectivity_mean+sd_c), width=.2,
                position=position_dodge(.9)) +
  xlab("Grasp Competence") + ylab("ISPC visual-motor network (anticipation)") + labs(fill = "Condition")
p_bar 
ggsave('Bar_ISPCnormWB_PC_groupcompetence_-1000-500_cl15.png', plot = last_plot(), device = 'png', scale = 0.75, width = 7, height = 4, path = path_mac_new)


## FOR STATISTICS
d_con_beh_oc <- d_con_beh[!is.na(d_con_beh$GraspLat),]%>%
  filter(ChanPair == "OC")%>%
  mutate(group_competence = ifelse(GraspLat > median_comp, "Slow", "Fast"))

# STATISTICS FOR EACH CHANNEL PAIR (ANOVA BASED ON GROUP COMPETENCE)
Anov_oc <- ezANOVA(data=d_con_beh_oc, dv = Connectivity, wid = Participant, within = .(Condition), between = .(group_competence), type = 3, detailed = TRUE)  # build
show(Anov_oc)

## TO CALCULATE EFFECT SIZE (PARTIAL ETA SQUARE)
Anov_oc$ANOVA$PartialEta = Anov_oc$ANOVA$SSn/(Anov_oc$ANOVA$SSn + Anov_oc$ANOVA$SSd) # To compute residuals for each effect!
show(Anov_oc)


# Z-TEST for the only model that show a difference based on grasp competence
d_con_beh_oc_fast <- d_con_beh_oc %>%
  filter(group_competence == "Fast" & Condition == "cane")

d_con_beh_oc_slow <- d_con_beh_oc %>%
  filter(group_competence == "Slow" & Condition == "cane")

t.test(d_con_beh_oc_fast$Connectivity)
t.test(d_con_beh_oc_slow$Connectivity)

d_con_beh_oc_fast <- d_con_beh_oc %>%
  filter(group_competence == "Fast" & Condition == "grasp")

d_con_beh_oc_slow <- d_con_beh_oc %>%
  filter(group_competence == "Slow" & Condition == "grasp")

t.test(d_con_beh_oc_fast$Connectivity)
t.test(d_con_beh_oc_slow$Connectivity)


d_con_beh_oc_fast <- d_con_beh_oc %>%
  filter(group_competence == "Fast")
d_con_beh_oc_slow <- d_con_beh_oc %>%
  filter(group_competence == "Slow")
t.test(d_con_beh_oc_fast$Connectivity)
t.test(d_con_beh_oc_slow$Connectivity)


```


## CHECK RELATIONS BETWEEN WHOLE BRAIN CONNECTIVITY AND BEHAVIOR

```{r thetanormWB, echo=FALSE}

## SUMMARIZE DATA
lbls <- c('-1000:-500', '-500:0', '0:500', '500:1000')
#lbls <- c('-2000:-1500','-1500:-1000','-1000:-500 ms', '-500:0 ms','0:-500 ms', '500:1000 ms')
min_time <- -1000
max_time <- 1000

sum_all_stats <- data_wb_all%>%
  filter(Time>min_time & Time<=max_time)%>%
  group_by(TimeGroup = cut(Time, 
              breaks = seq(min_time, max_time, by = 500), labels = lbls), Condition, Age, Participant)%>%
  group_by(Condition, Age, Participant, TimeGroup)%>%
  #group_by(Condition, Age, Participant)%>% #If we don't want to define time windows
  summarise(mean_stats = mean(Threshold))

#sum_all_stats_t2 <- sum_all_stats # if all time window. If not, use following code
sum_all_stats_t2 <- sum_all_stats %>%
  filter(TimeGroup == lbls[1])

######################################################################
######################################################################
## LINK TO BEHAVIOR
## FIRST, PREPARE DATA
sum_all_stats_wide<- sum_all_stats_t2 %>%
  pivot_wider(names_from = c(Condition), values_from = mean_stats)

sum_all_stats_wide<- rowid_to_column(sum_all_stats_wide)

d_con_beh <- merge(sum_all_stats_wide,d_behavior, by = "rowid")%>%
  select(-c(rowid, subnum))%>%
  pivot_longer(
  cols = Cane:Grasp,
  names_to = "Condition",
  values_to = "Connectivity")%>%
  mutate(GraspLat = Competence_NEW_Grasp/1000)%>%
  mutate(CaneLat = Competence_NEW_Cane/1000)

## NOW, LINK IT TO BEHAVIOR
## 1. GRASP LATENCY
d_con_beh_noNaN <- d_con_beh[!is.na(d_con_beh$GraspLat),]
#  filter(Condition == "Grasp") ## remove subjects with NaN 
  
p_data <- ggplot(d_con_beh_noNaN, aes(x=GraspLat, y=Connectivity, shape=Condition, colour=Condition, fill=Condition)) + geom_point(shape=1) +     # Use hollow circles
  geom_smooth(method=lm) + ylab("WHOLE BRAIN ISPC") + xlab("Grasp Latency (s)") + facet_grid(. ~ Age)
p_data

## LINEAR MODEL GRASP COMPETENCE AND CONNECTIVITY
## MIXED EFFECT MODELS
# BASIC MODEL
m.0 <- lmer(Connectivity ~ Condition + (1 | Participant) , data=d_con_beh_noNaN, REML = FALSE)  # build

# ADD THE NEXT MORE "OBVIOUS" VARIABLE
m.1_0 <- update(m.0, .~. + Age) 
m.1_1 <- update(m.1_0, .~. + Age*Condition)

m.2_0 <- update(m.1_1, .~. + GraspLat) 
m.2_1 <- update(m.2_0, .~. + GraspLat*Condition)
m.2_2 <- update(m.2_0, .~. + GraspLat*Age*Condition)

anova(m.0,m.1_0,m.1_1,m.2_0,m.2_1,m.2_2) # 2_0 is not sign


## 2. CANE SUCCESS
d_con_beh_noNaN <- d_con_beh[!is.na(d_con_beh$CaneLat),]
#  filter(Condition == "Cane") ## remove subjects with NaN 
  
p_data <- ggplot(d_con_beh_noNaN, aes(x=CaneLat, y=Connectivity, shape=Condition, colour=Condition, fill=Condition)) +
  geom_point(shape=1) +     # Use hollow circles
  geom_smooth(method=lm) + ylab("WHOLE BRAIN ISPC: -2000 to 1000ms") + xlab("Cane Latency (s)") + facet_grid(. ~ Age)
p_data 
#ggsave('wholebrainVSCaneLat_acrosstime_Allwin_age_new.png', plot = last_plot(), device = 'png', scale = 0.7, width = 10, height = 7, path = path_mac_new)

## MIXED EFFECT MODELS
# BASIC MODEL
m.0 <- lmer(Connectivity ~ Condition + (1 | Participant) , data=d_con_beh_noNaN, REML = FALSE)  # build

# ADD THE NEXT MORE "OBVIOUS" VARIABLE
m.1_0 <- update(m.0, .~. + Age) 
m.1_1 <- update(m.1_0, .~. + Age*Condition)

m.2_0 <- update(m.1_1, .~. + CaneLat) 
m.2_1 <- update(m.2_0, .~. + CaneLat*Condition)
m.2_2 <- update(m.2_0, .~. + CaneLat*Age*Condition)

anova(m.0,m.1_0,m.1_1,m.2_0,m.2_1,m.2_2) # 2_0 is not sign

```


## CHECK RELATIONS BETWEEN WHOLE BRAIN AND CHANNEL PAIR NETWORKS

```{r thetanormWB, echo=FALSE}

## SUMMARIZE DATA

lbls <- c('-1000:-500 ms', '-500:0 ms', 
          '0:-500 ms', '500:1000 ms')
min_time <- -1000
max_time <- 1000

sum_all_stats <- data_all_with_wb%>%
  filter(Time>min_time & Time<=max_time)%>%
  group_by(TimeGroup = cut(Time, 
               breaks = seq(min_time, max_time, by = 500), labels = lbls), Condition, Age, Participant, ChannelPair)%>%
  summarise(mean_stats = mean(connectivity_norm), mean_wb = mean(Threshold)) # NO NORMALIZED

sum_all_stats_t2 <- sum_all_stats %>%
  filter(TimeGroup == lbls[1])

######################################################################
######################################################################
## LINK TO BEHAVIOR

## 1. GRASP 
d_con_fil <- filter(sum_all_stats_t2,Condition == "grasp")
p_data <- ggplot(d_con_fil, aes(x=mean_wb, y=mean_stats, color = Age, shape = Age, fill=Age)) +
  geom_point(shape=1) +     # Use hollow circles
  geom_smooth(method=lm) + facet_grid(. ~ ChannelPair) + ylab("ISPC Grasp") + xlab("ISPC Whole Brain ")
p_data
ggsave('ChanPairvsWB_acrosstime_grasp_-1000-500.png', plot = last_plot(), device = 'png', scale = 0.7, width = 13, height = 6, path = path_mac_new)

d_con_fil_oc <- filter(d_con_fil,ChannelPair == "OC")
d_con_fil_pc <- filter(d_con_fil,ChannelPair == "PC")
d_con_fil_fc <- filter(d_con_fil,ChannelPair == "FC")

lm_grasp_oc <- lm(mean_stats ~ mean_wb*Age, data=d_con_fil_oc)  # build
summary(lm_grasp_oc)

lm_grasp_pc <- lm(mean_stats ~ mean_wb*Age, data=d_con_fil_pc)  # build
summary(lm_grasp_pc)
lm_grasp_fc <- lm(mean_stats ~ mean_wb*Age, data=d_con_fil_fc)  # build
summary(lm_grasp_fc)

# BASIC MODEL = CHANNEL PAIR
m.0 <- lmer(mean_stats ~ ChannelPair + (1 | Participant), data=d_con_fil, REML = FALSE)  # build

# ADD THE NEXT MORE "OBVIOUS" VARIABLE
m.1_0 <- update(m.0, .~. + Age) 
m.1_1 <- update(m.1_0, .~. + Age*ChannelPair)

# FINALLY WE ADD WB
m.2_0 <- update(m.1_1, .~. + mean_wb)
m.2_1 <- update(m.2_0, .~. + mean_wb*ChannelPair)
m.2_2 <- update(m.2_0, .~. + mean_wb*ChannelPair*Age)

anova(m.0,m.1_0, m.1_1, m.2_0,m.2_1, m.2_2) # 2_0 is not sign

anova(m.2_0)
summary(m.2_0)


## 2. CANE
d_con_fil <- filter(sum_all_stats_t2,Condition == "cane")
p_data <- ggplot(d_con_fil, aes(x=mean_wb, y=mean_stats, shape=Age, colour=Age, fill=Age)) +
  geom_point(shape=1) +     # Use hollow circles
  geom_smooth(method=lm) + facet_grid(. ~ ChannelPair)  + ylab("ISPC Cane") + xlab("ISPC Whole Brain ")
p_data
ggsave('ChanPairvsWB_acrosstime_cane_-1000-500.png', plot = last_plot(), device = 'png', scale = 0.7, width = 13, height = 6, path = path_mac_new)

d_con_fil_oc <- filter(d_con_fil,ChannelPair == "OC")
d_con_fil_pc <- filter(d_con_fil,ChannelPair == "PC")
d_con_fil_fc <- filter(d_con_fil,ChannelPair == "FC")

lm_cane_oc <- lm(mean_stats ~ mean_wb*Age, data=d_con_fil_oc)  # build
summary(lm_cane_oc)
lm_cane_pc <- lm(mean_stats ~ mean_wb*Age, data=d_con_fil_pc)  # build
summary(lm_cane_pc)
lm_cane_fc <- lm(mean_stats ~ mean_wb*Age, data=d_con_fil_fc)  # build
summary(lm_cane_fc)


# BASIC MODEL = CHANNEL PAIR
m.0 <- lmer(mean_stats ~ ChannelPair + (1 | Participant), data=d_con_fil, REML = FALSE)  # build

# ADD THE NEXT MORE "OBVIOUS" VARIABLE
m.1_0 <- update(m.0, .~. + Age) 
m.1_1 <- update(m.1_0, .~. + Age*ChannelPair)

# FINALLY WE ADD WB
m.2_0 <- update(m.1_1, .~. + mean_wb)
m.2_1 <- update(m.2_0, .~. + mean_wb*ChannelPair)
m.2_2 <- update(m.1_1, .~. + mean_wb*ChannelPair*Age)

anova(m.0,m.1_0,m.1_1,m.2_0,m.2_1, m.2_2) # 2_0 is not sign

anova(m.2_0)
summary(m.2_0)


```


## CORRELATE CONNECTIVITY (ISPC across time normalized by whole brain threshold) AND POWER

```{r thetanormWB, echo=FALSE}

## SUMMARIZE DATA

lbls <- c('-1000:-500 ms', '-500:0 ms', 
          '0:-500 ms', '500:1000 ms')
min_time <- -1000
max_time <- 1000

sum_all_stats <- data_all_with_wb%>%
  filter(Time>min_time & Time<=max_time)%>%
  #mutate(TimeGroup = cut(Time, breaks = seq(min_time, max_time, by = 500), labels = lbls))
  group_by(TimeGroup = cut(Time, 
               breaks = seq(min_time, max_time, by = 500), labels = lbls), Condition, Age, Participant, ChannelPair)%>%
  summarise(mean_stats = mean(connectivity_norm))

sum_all_stats_t2 <- sum_all_stats %>%
  filter(TimeGroup == lbls[1])

######################################################################
######################################################################
## LINK TO BEHAVIOR

## FIRST, PREPARE DATA
sum_all_stats_wide<- sum_all_stats_t2 %>%
  pivot_wider(names_from = c(Condition,ChannelPair), values_from = mean_stats)

sum_all_stats_wide<- rowid_to_column(sum_all_stats_wide)


d_behavior <- read.csv("LAEEG_power_results_R.csv", sep=",")
d_behavior<- rowid_to_column(d_behavior)

d_con_power <- merge(sum_all_stats_wide,d_behavior, by = "rowid")%>%
  select(-c(TimeGroup, rowid, Subj))%>%
  pivot_longer(
  cols = cane_FC:grasp_OC,
  names_to = "Condition.ChanPair",
  values_to = "Connectivity"
)%>%
  separate(Condition.ChanPair,c("Condition", "ChanPair"))

## NOW, LINK IT TO POWER

## 1. GRASP 
d_con_fil <- filter(d_con_power,Condition == "grasp")
p_data <- ggplot(d_con_fil, aes(x=Connectivity, y=Grasp.Mu.1000500, shape=Age, colour=Age, fill=Age)) +
  geom_point(shape=1) +     # Use hollow circles
  geom_smooth(method=lm) + facet_grid(. ~ ChanPair) + ylab("Mu Power Grasp") + xlab("ISPC across time")
p_data
ggsave('ChanPair_normWbvsPower_acrosstime_grasp_-1000-500.png', plot = last_plot(), device = 'png', scale = 0.8, width = 11, height = 9, path = path_mac_new)

linearMod_grasp <- lm(Grasp.Mu.1000500 ~ Connectivity*Age*ChanPair, data=d_con_fil)  # build
summary(linearMod_grasp)

## 2. CANE
d_con_fil <- filter(d_con_power,Condition == "cane")
p_data <- ggplot(d_con_fil, aes(x=Connectivity, y=Cane.Mu.1000500, shape=Condition, colour=Age, fill=Age)) +
  geom_point(shape=1) +     # Use hollow circles
  geom_smooth(method=lm) + facet_grid(. ~ ChanPair)  + ylab("Mu Power Cane") + xlab("ISPC across time")
p_data
ggsave('ChanPair_normWbvsPower_acrosstime_cane_-1000-500.png', plot = last_plot(), device = 'png', scale = 0.8, width = 11, height = 9, path = path_mac_new)

linearMod_cane <- lm(Cane.Mu.1000500 ~ Connectivity*Age*ChanPair, data=d_con_fil)  # build
summary(linearMod_cane)


```


